\huge A Usability Evaluation of Tor Launcher

### 2016-10-28 pets2017-paper/pets2017-paper.tex
add number of researchers involved in formative testing

\subsection{Procedure}
Before the experiment began, each participant was verbally informed of the purpose of the 
study, what data was collected, and any associated risks. If they wished to participate,
they were informed again in writing and consented by signing the document. To be thorough, 
we clarified verbally that they could stop at any time during the experiment with no negative consequences.

>>>>

\subsection{Procedure}
Three researchers ran the formative usability testing, with each session having at least two researchers.  
Before the experiment began, each participant was verbally informed of the purpose of the 
study, what data was collected, and any associated risks. If they wished to participate,
they were informed again in writing and consented by signing the document. To be thorough, 
we clarified verbally that they could stop at any time during the experiment with no negative consequences.
